### 2025-03-05 tutorials/getstarted.qmd
Rephrase the inner product point.

In a nutshell a Lie group $𝒢$ is a [manifold](https://en.wikipedia.org/wiki/Manifold) $ℳ$ that also is a group with a group operation.
A manifold can informally be described as a set that “locally looks like a Euclidean space”
and has some way to measure angles at every point, to be precise an inner product, that is allowed to (smoothly)
depend on the point we are at.
A [group](https://en.wikipedia.org/wiki/Group_(mathematics)) means that on the set there also
exists an operation, within this package usually denoted by $∘: 𝒢 × 𝒢 → 𝒢$,
`LieGroups.jl` uses the manifolds defined in [`Manifolds.jl`](https://juliamanifolds.github.io/Manifolds.jl/stable/). For more details on that, see also the [introductory tutorial](https://juliamanifolds.github.io/Manifolds.jl/stable/tutorials/getstarted/) there.
A Lie group is usually written as a tuple $(ℳ,∘)$ with the manifold and the group operation thereon.

>>>>

In a nutshell a Lie group $𝒢$ is a [manifold](https://en.wikipedia.org/wiki/Manifold) $ℳ$ that also is a group with a group operation.

A manifold can informally be described as a set that “locally looks like a Euclidean space”
and has some way to measure angles at every point.
Formally, this yields an inner product that depends (smoothly) on the point one is at.
For Lie groups this will be a bit easier.

A [group](https://en.wikipedia.org/wiki/Group_(mathematics)) means that on the set there also
exists an operation, within this package usually denoted by $∘: 𝒢 × 𝒢 → 𝒢$,
`LieGroups.jl` uses the manifolds defined in [`Manifolds.jl`](https://juliamanifolds.github.io/Manifolds.jl/stable/). For more details on that, see also the [introductory tutorial](https://juliamanifolds.github.io/Manifolds.jl/stable/tutorials/getstarted/) there.
A Lie group is usually written as a tuple $(ℳ,∘)$ with the manifold and the group operation thereon.
